Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-03 paper/comoving-followup.tex
add GP kernel refs

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{sample_cmd.pdf}
  \end{center}
  \caption{%
    Color-magnitude diagram for all \tgas\ sources within $200~\pc$ (blue
    histogram) and all comoving star pair members observed in this follow-up
    effort (black points); lines (orange) connect comoving pairs of stars.
    2MASS $J$-band magnitudes are obtained from the Gaia science
    archive.
    Apparent $G$-band magnitudes (\citealt{Carrasco:2016}) are converted to
    absolute magnitude, $M_G$, using a Lutz-Kelker-corrected
    (\citealt{Lutz:1973}) distance estimate (see also \eqname~1 in
    \citealt{Oh:2017}).
    \label{fig:sample-cmd}}
\end{figure}

@@

We start the wavelength calibration by interactively identifying the 12
strongest, least blended emission lines in one of the extracted 1D comparison
lamp spectra by comparing to \todo{NIST??}.
Once a rough mapping from pixel to wavelength is determined, we then fit for
the individual line centroids in each comparison lamp spectrum by extracting
small, 8 pixel-wide segments of spectrum around each identified emission line
and fitting a model for the line profile and background to each individually.
We use a Gaussian profile for each emission line with parameters: amplitude,
$A$; centroid, $x_0$; and root-variance, $\sigma_G$.
We found that nearby blended or low-amplitude lines (i.e. part of the
``background'') sometimes bias the line centroid determination when using a
simple background model.
We therefore model the background flux around each comparison lamp emission
line using a constant offset + Gaussian process (GP) with a Mat\'ern 3/2 kernel
parametrized by amplitude parameter $\sigma_{3/2}$ and correlation scale
$\rho_{3/2}$.
We use \package{celerite} (\citealt{Foreman-Mackey:2017}) to evaluate the full
likelihood, and maximize the (log-)likelihood again using \lbfgsb\
optimization.
We optimize over the logarithm of any scale parameters (i.e. $A$, $\sigma_G$,
$\sigma_{3/2}$, and $\rho_{3/2}$).
Once we determine the pixel centroids for all identified emission lines for a
given night's comparison lamp spectrum, we then fit an interpolating function
to the pixel-centroid, wavelength values for each emission line.

>>>>

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{sample_cmd.pdf}
  \end{center}
  \caption{%
    Color-magnitude diagram for all \tgas\ sources within $200~\pc$ (background
    blue histogram) and all comoving star pair members observed in this
    follow-up effort (black points); colored lines connect candidate comoving
    star pairs.
    2MASS $J$-band magnitudes are obtained from the Gaia science
    archive.
    Apparent $G$-band magnitudes (\citealt{Carrasco:2016}) are converted to
    absolute magnitude, $M_G$, using a Lutz-Kelker-corrected
    (\citealt{Lutz:1973}) distance estimate (see also \eqname~1 in
    \citealt{Oh:2017}).
    \label{fig:sample-cmd}}
\end{figure}

@@

We start the wavelength calibration by interactively identifying the 12
strongest, least blended emission lines in one of the extracted 1D comparison
lamp spectra by comparing to \todo{NIST??}.
Once a rough mapping from pixel to wavelength is determined, we then fit for
the individual line centroids in each comparison lamp spectrum by extracting
small, 8 pixel-wide segments of spectrum around each identified emission line
and fitting a model for the line profile and background to each individually.
We use a Gaussian profile for each emission line with parameters: amplitude,
$A$; centroid, $x_0$; and root-variance, $\sigma_G$.
We find that nearby blended or low-amplitude lines (i.e. part of the
``background'') sometimes bias the line centroid determination when using a
simple background model.
We therefore model the background flux around each comparison lamp emission
line using a constant offset + Gaussian process (GP).
For the GP model, we use a Mat\'ern 3/2 kernel function
(\citealt{Matern:1986,Rasmussen:2005}) parametrized by amplitude parameter
$\sigma_{3/2}$ and correlation scale $\rho_{3/2}$.
We use \package{celerite} (\citealt{Foreman-Mackey:2017}) to evaluate the full
likelihood for this model, and maximize the (log-)likelihood again using
\lbfgsb\ optimization.
We optimize over the logarithm of any scale parameters (i.e. $A$, $\sigma_G$,
$\sigma_{3/2}$, and $\rho_{3/2}$).
Once we determine the pixel centroids for all identified emission lines for a
given night's comparison lamp spectrum, we then fit an interpolating function
to the pixel-centroid, wavelength values for each emission line.
